Application with Different Lakes Data

### 2021-07-28 inst/scripts/application2.Rmd
sloppy html file of application.
modified documentation and namespace so that package loads without errors, warnings, or notes.

```{r}
library(tidyverse)
library(here)
library(sptotal)
library(skimr)
nla_df <- read_csv(here("data", "nla12_keyvariables_data.csv"))
skim(nla_df)
```

```{r}
View(nla_df)
factor(nla_df$TOTALHG_UNITS) ## all same units
```

>>>>

```{r}
library(tidyverse)
library(here)
library(sptotal)
library(skimr)
load(here("data", "nla.rda"))
```

```{r, results = "hide", eval = FALSE}
View(nla_df)
factor(nla_df$TOTALHG_UNITS) ## all same units
```
